---
title: "ODA Analysis Pipeline"
author: "H.S"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)

crs <- read_csv("crs_disbursements.csv") %>% clean_names()
wdi <- read_csv("wdi_indicators.csv") %>% clean_names()
pop <- read_csv("pop_income.csv") %>% clean_names()

merged <- crs %>%
group_by(recipient, year = as.integer(time_period)) %>%
summarise(oda_total = sum(obs_value, na.rm = TRUE), .groups = "drop")

summary(merged)

ggplot(merged, aes(x = year, y = oda_total)) +
geom_line(color = "steelblue") +
theme_minimal() +
labs(title = "Total ODA over Time", x = "Year", y = "ODA (USD)")
```
```{r fig.width=6, fig.height=4, echo=FALSE}
ggplot(merged, aes(x = year, y = oda_total)) +
  geom_line(color = "steelblue") +
  theme_minimal() +
  labs(title = "Total ODA over Time", x = "Year", y = "ODA (USD)")
```

## Results

The figure above shows changes in total ODA by year.  
A clear upward trend indicates that aid volumes increased during the observed period.  
Further analysis can separate education-related ODA or normalize data by population size.

## Conclusion

This report demonstrates a simple data pipeline that:
- Cleans and merges CRS, WDI, and population datasets  
- Aggregates yearly ODA totals  
- Visualizes ODA trends over time  

Future work could include regression modeling or adding indicators such as literacy and GDP per capita to examine relationships between aid and development outcomes.



